---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hyper

This experimental package is meant to enable composition of HTML, CSS, and JavaScript using piped functions. A key consideration is for flexible composability: use HTML-constructing functions, use HTML fragments or Markdown, use R objects or functions to bind data, and also use nested pipelines for less typing.

## Installation

You can install hyper from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("rich-iannone/hyper")
```

If you encounter a bug or want to share ideas to make this package better, feel free to file an [issue](https://github.com/rich-iannone/hyper/issues).

## Code of Conduct

[Contributor Code of Conduct](https://github.com/rich-iannone/hyper/blob/master/CONDUCT.md). By participating in this project you agree to abide by its terms.

## License

MIT &copy; Richard Iannone
